So you've decided to detonate helium

### 2020-03-21 sdc_applications/paper.tex
some minor edits

\shorttitle{Detonations and NSE}
\shortauthors{Zingale et al.}

@@

\castro\ has the ability to reject a timestep if it detects a failure
and retry with smaller timesteps (subcycling to make up the original
required timestep).  Among the conditions that can trigger this are
density failing below zero during advection, the VODE integration
failing to converge in the implicit solve, or violation of one of the
timestep limiters during the step.  At the moment, this retry
mechanism only works with the CTU hydrodynamics + Strang splitting.
We enable it here, since, as will be shown shortly, this combination
of methods has the most difficulty in integrating the detonation.

@@

\subsection{SDC Method}

A second-order accurate time integration method using a simple
deferred correction strategy was shown in \citep{nonaka:2016}.  A
version of this was also implemented in the \maestro\ low-Mach number
hydrodynamics code some time ago.  A compressible version, for use in
\castro\ is slightly different due to the need to do some operations
on the conserved variable state and some on the primitive variable
state.  We describe the application of this to the equations of
compressible hydrodynamics below:

@@

\section{Detonations}

@@

@@

\software{\amrex\ (\url{https://github.com/AMReX-Codes/amrex}),
          \castro\ \citep{castro},
          GNU Compiler Collection (\url{https://gcc.gnu.org/}),
          Linux (\url{https://www.kernel.org}),
          matplotlib (\citealt{Hunter:2007},  \url{http://matplotlib.org/})
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/})
         }

@@

To solve the reaction system implicitly, the ODE solver needs the Jacobian,
$\partial \Rb/\partial \Uc$.  We follow the method of \cite{castro_sdc}
and factor this into two pieces,
\begin{equation}
{\bf J} = \partial \Rb/\partial {\bf w } \partial {\bf w}/\partial \Uc
\end{equation}.

>>>>

\shorttitle{Detonations and NSE}
\shortauthors{}

@@

\castro\ has the ability to reject a timestep if it detects a failure
and retry with smaller timesteps (subcycling to make up the original
required timestep).  Among the conditions that can trigger this are
density failing below zero during advection, the ODE integration
failing to converge in the implicit solve, or violation of one of the
timestep limiters during the step.  At the moment, this retry
mechanism only works with the CTU hydrodynamics + Strang splitting.
We enable it here, since, as will be shown shortly, this combination
of methods has the most difficulty in integrating the detonation.

@@

\subsection{Spectral Deferred Corrections}

The basic idea of spectral deferred corrections is break the timestep
into a number of temporal nodes and use low order difference methods
in a correction equation that, upon iteration, achieves a high-order
solution coupling the different physics together.

\subsection{Simplified-SDC Method}

A second-order accurate time integration method using a simple
deferred correction strategy was shown in \citep{SDC-old}.  A
version of this was also implemented in the \maestro\ low-Mach number
hydrodynamics code some time ago.  A compressible version, for use in
\castro\ is slightly different due to the need to do some operations
on the conserved variable state and some on the primitive variable
state.  We describe the application of this to the equations of
compressible hydrodynamics below:

@@

\section{Simulations}

\subsection{Flames}

ECSNe flames

\subsection{Detonations}

@@

\subsection{Hydro and Gravity}

Merging stars

@@

\software{\amrex\ \citep{amrex_joss},
          \castro\ \citep{castro},
          GNU Compiler Collection (\url{https://gcc.gnu.org/}),
          Linux (\url{https://www.kernel.org}),
          matplotlib (\citealt{Hunter:2007},  \url{http://matplotlib.org/})
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/})
         }

@@

To solve the reaction system implicitly, the ODE solver needs the Jacobian,
$\partial \Rb/\partial \Uc$.  We follow the method of \cite{castro_sdc}
and factor this into two pieces,
\begin{equation}
{\bf J} = \frac{\partial \Rb}{\partial {\bf w }} \frac{\partial {\bf w}}{\partial \Uc}
\end{equation}.
